\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}
\usepackage{enumitem}

\title{Ultimate Disc App Technology Plan}
\author{Project Planning}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This document outlines the technology stack and planning considerations for the Ultimate Disc App, a web application for managing a student-led Ultimate Disc club. The plan covers all components, with a focus on the team allocation system as the core functionality.

\section{Component Breakdown and Technology Choices}

\subsection{Player Dashboard}
\begin{itemize}
    \item \textbf{Purpose:} User interface for players to log in, check in, view team assignments, trophies, and session history.
    \item \textbf{Technologies:}
    \begin{itemize}
        \item React (JSX) via CDN for component-based UI.
        \item Tailwind CSS for responsive styling.
        \item JavaScript (ES6+) with Babel for browser compatibility.
    \end{itemize}
\end{itemize}

\subsection{Admin Dashboard}
\begin{itemize}
    \item \textbf{Purpose:} Manages players, sessions, team drafts, and trophies with real-time updates.
    \item \textbf{Technologies:}
    \begin{itemize}
        \item React (JSX) + Tailwind CSS for consistency with player dashboard.
        \item React Beautiful DnD or Dnd-kit for drag-and-drop team adjustments.
        \item Socket.IO for live attendance updates.
    \end{itemize}
\end{itemize}

\subsection{Team Allocation System}
\begin{itemize}
    \item \textbf{Purpose:} Allocates players into balanced teams based on class, skill, and shirt color.
    \item \textbf{Technologies:}
    \begin{itemize}
        \item JavaScript (Node.js) for algorithm implementation, using array methods for sorting and filtering.
        \item Integrated with React front end and Express back end.
    \end{itemize}
    \item \textbf{Rationale:} JavaScript ensures seamless integration with the web stack, avoiding overhead of languages like Python or C++.
\end{itemize}

\subsection{Trophy System}
\begin{itemize}
    \item \textbf{Purpose:} Handles trophy submissions, custom trophy creation, and approvals.
    \item \textbf{Technologies:}
    \begin{itemize}
        \item React + Tailwind CSS for forms and approval tables.
        \item Node.js (Express) for processing submissions.
        \item REST API for front-end/back-end communication.
    \end{itemize}
\end{itemize}

\subsection{Data Storage}
\begin{itemize}
    \item \textbf{Purpose:} Stores player profiles, sessions, trophies, and results.
    \item \textbf{Technologies:}
    \begin{itemize}
        \item PostgreSQL for relational data storage.
        \item Prisma or Sequelize for ORM to simplify database interactions.
    \end{itemize}
\end{itemize}

\subsection{Back End}
\begin{itemize}
    \item \textbf{Purpose:} Manages authentication, API endpoints, and real-time updates.
    \item \textbf{Technologies:}
    \begin{itemize}
        \item Node.js + Express for lightweight API development.
        \item JWT for secure authentication.
        \item Socket.IO for real-time updates.
    \end{itemize}
\end{itemize}

\subsection{Deployment}
\begin{itemize}
    \item \textbf{Technologies:}
    \begin{itemize}
        \item Vercel or Netlify for front-end hosting.
        \item Heroku or Render for back-end and database hosting.
    \end{itemize}
\end{itemize}

\subsection{Additional Tools}
\begin{itemize}
    \item Babel for JavaScript compatibility.
    \item ESLint for code quality.
    \item Vite for fast development and bundling.
\end{itemize}

\section{Rationale}
\begin{itemize}
    \item \textbf{JavaScript Stack:} Unifies front and back end, simplifying development.
    \item \textbf{React + Tailwind:} Ensures scalable, responsive UI.
    \item \textbf{PostgreSQL:} Matches structured data needs.
    \item \textbf{WebSockets:} Enables real-time updates for admin dashboard.
    \item \textbf{Deployment:} Vercel and Heroku simplify browser-based access.
\end{itemize}

\section{Next Steps}
\begin{enumerate}
    \item Prototype team allocation algorithm in JavaScript, addressing edge cases.
    \item Design wireframes for dashboards.
    \item Define PostgreSQL schema for players, sessions, and trophies.
    \item Prioritize MVP features (allocation, dashboards) before adding MVP ranking.
\end{enumerate}

\end{document}